Is Vagueness Beneficial for Hearers? \protect \\ Evidence from Experiments

### 2016-09-25 papers/2016-Special-Issue/v-special-issue-2016.tex
e1 results graph has more readable text

\documentclass[doc,floatsintext,apacite]{apa6}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{color}
\usepackage{booktabs}
\usepackage{layout}
\usepackage{apacite}
\usepackage{datetime}
\usepackage{rotating} % comment out for man mode

\renewcommand{\baselinestretch}{1.7} % added 21 Sept 2016, copied from CRM book

@@

\begin{figure}[htbp]
\fitfigure{images/resultse1.pdf}
\caption{Experiment 1 results: response times and error rates}
\label{resultse1}
\end{figure}

@@

\begin{table}[tbp]
\caption{Table of instructions arranged by condition for the triple (6,15,24)}
\label{instre3}
\begin{tabular}{rll}
&crisp&vague\\
\hline
numerical	&		Choose the square with 6 dots 			& 	Choose a square with about 10 dots			\\
verbal	&		Choose the square with the fewest dots	&	Choose a square with few dots\\
\end{tabular}
\end{table}

\subsection{Hypotheses}
(H1) A main effect RT advantage for vagueness.

(H2) An RT advantage for vagueness both in \emph{numeric} and in \emph{verbal} instructions.

(H3) No large main effect of instruction format (numeric versus verbal). 
%MG If we are right that vagueness was responsible for the vagueness advantage in e 1, that could also have been a number avoidance advantage, then we would not expect that number avoidance, or, instruction format, plays a role (?)

(H4) On the basis of Experiment 1, we would expect faster responses to more discriminable triples (i.e., an effect of triple).

(H5) Participants should make more borderline case choices for vague than crisp instructions.

@@

\begin{table}[htbp]
\centering
\caption{Experiment 3: Instructions, assuming $6,15,24$ dots as the Item} %, and showing \emph{fewer} instead of \emph{more}}
\label{Instructions for e3}
\begin{tabular}{llll}
\hline
vagueness&instruction format&selection task&instruction\\
\hline
crisp 	& numeric		&	matching		& Choose a square with 6 dots \\ 
crisp 	& numeric		&	comparison 	& Choose a square with fewer than 20 dots \\
vague	& numeric		&	matching 		& Choose a square with about 10 dots \\ 
vague 	& numeric		&	comparison 	& Choose a square with far fewer than 20 dots \\ 
\hline
\end{tabular}
\end{table}%

@@

\begin{table}[htbp]
\centering
\caption{Experiment 4: Instructions}
\label{Instructions for e4}
\begin{tabular}{lllp{7cm}}
\hline
vagueness&instruction format& selection task&instruction\\
\hline
crisp 	& verbal	&	matching 		& Choose a square with the same number of dots as the target \\ 
crisp 	& verbal	&	comparison	& Choose a square with fewer dots than the target \\
vague 	& verbal	&	matching 		& Choose a square with about the same number of dots as the target \\ 
vague 	& verbal	&	comparison	& Choose a square with far fewer dots than the target \\ 
\hline
\end{tabular}
\end{table}%

@@

>>>>

\documentclass[%
doc,% saying man here makes it doublespaced; saying doc here instead makes it singlespaced again as supported by the documentclass
floatsintext,%
apacite%
]{apa6}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{color}
\usepackage{booktabs}
\usepackage{layout}
\usepackage{apacite}
\usepackage{datetime}

%\renewcommand{\baselinestretch}{1.7} % added 21 Sept 2016, copied from CRM book

@@

\begin{figure}[htbp]
\fitfigure{images/plotRTandErrorRates-1}
\caption{Experiment 1 results: response times and error rates}
\label{resultse1}
\end{figure}

@@

\begin{table}[tbp]
\caption{Experiment 1: instructions arranged by condition for the dot triple $(6,15,24)$ and instructions indicating the smaller numbers}
\label{instre3}
\begin{tabular}{rll}
&crisp&vague\\
\midrule
numerical	&		Choose the square with 6 dots 			& 	Choose a square with about 10 dots			\\
verbal	&		Choose the square with the fewest dots	&	Choose a square with few dots\\
\midrule
\end{tabular}
\end{table}

\begin{APAenumerate}
	\item [(H1)] A main effect RT advantage for vagueness.
	\item [(H2)] An RT advantage for vagueness both in \emph{numeric} and in \emph{verbal} instructions.
	\item [(H3)] No large main effect of instruction format (numeric versus verbal).
	\item [(H4)] On the basis of Experiment 1, we would expect faster responses to more discriminable triples (i.e., an effect of triple).
	\item [(H5)] Participants should make more borderline case choices for vague than crisp instructions.
\end{APAenumerate}

@@

\begin{table}[htbp]
\centering
\caption{Experiment 3: Instructions arranged by condition for the dot triple $(6,15,24)$and instructions indicating the smaller numbers} %, and showing \emph{fewer} instead of \emph{more}}
\label{Instructions for e3}
\begin{tabular}{llll}
vagueness	&	instruction		&	selection	&	instruction\\
			&	format		&	task		&			\\
\toprule
\multirow{ 2}{*}{crisp} 	& \multirow{ 2}{*}{numeric}	&	matching		& Choose a square with 6 dots \\ 
					& 						&	comparison 	& Choose a square with fewer than 20 dots \\
					\midrule
\multirow{ 2}{*}{vague} 	& \multirow{ 2}{*}{numeric} 	&	matching 		& Choose a square with about 10 dots \\ 
 					& 						&	comparison 	& Choose a square with far fewer than 20 dots \\ 
\bottomrule
\end{tabular}
\end{table}%

@@

\begin{table}[htbp]
\centering
\caption{Experiment 4: Instructions}
\label{Instructions for e4}
\begin{tabular}{llll}
vagueness	&	instruction		&	selection							&	instruction: Choose a square with \ldots\\
			&	format		&	task		&			\\
\toprule
\multirow{ 2}{*}{crisp} 	 	& \multirow{ 2}{*}{verbal} 	&	matching 		& the same number of dots as the target \\ 
	& 	&	comparison										& fewer dots than the target \\
	\midrule
\multirow{ 2}{*}{vague} 	& \multirow{ 2}{*}{verbal} 	&	matching 			& about the same number of dots as the target \\ 
	& 	&	comparison										& far fewer dots than the target \\ 
\bottomrule
\end{tabular}
\end{table}%

@@

%(H1) A main effect RT advantage for vagueness.
%
%(H2) An RT advantage for vagueness both in \emph{numeric} and in \emph{verbal} instructions.
%
%(H3) No large main effect of instruction format (numeric versus verbal). 
%%MG If we are right that vagueness was responsible for the vagueness advantage in e 1, that could also have been a number avoidance advantage, then we would not expect that number avoidance, or, instruction format, plays a role (?)
%
%(H4) On the basis of Experiment 1, we would expect faster responses to more discriminable triples (i.e., an effect of triple).
%
%(H5) Participants should make more borderline case choices for vague than crisp instructions.
